Computer Science House By-Laws

### 2016-10-30 bylaws.tex
Change Packet Failure Effects
Failure to Get an Account After Packet is Failure to Complete Introductory Evaluations

	\item A signature from all Resident members who have passed a Membership Evaluation, each Executive Board member, all Resident Active members who have not passed a Membership Evaluation, all Resident Introductory members, and fifteen (15) of any combination of the following:

@@

@@

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required, non-Introductory signatures in the Introductory Packet or successfully complete Introductory Evaluations.
\end{enumerate}

>>>>

	\item A signature from all Active/Introductory Resident members, each Executive Board member, and fifteen (15) of any combination of the following:

@@

After the second week of the Introductory Packet, Introductory Members who have received less than 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) will have their membership revoked.

@@

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet.
\end{enumerate}
